---
title: "description statitics"
author: "Pengfei Luo"
date: "1/22/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
rm(list=ls())
library(tidyverse)
library(data.table)
library(psych)
```

Here we try several ways (packages) to summary descriptive statistics of data.(link: https://www.youtube.com/watch?v=ZA28sOmq7nU)

## load data
First, we load data from a local csv file. 
```{r}
pokemon <- as.data.table(read.csv("Pokemon.csv",stringsAsFactors = TRUE))
pokemon
str(as_tibble(pokemon))
```


## plot variables in dataframe
```{r}
# plot(pokemon)
plot(pokemon[,3:10])
plot(as_tibble(pokemon[,"Type.I"],pokemon[,'Atk']))
```






## descriptive statistics for our data, pokemon
### summary() function from basic package
```{r}
summary(pokemon)
```

### describe/describeBy functions from psych package
load *psych* package 
```{r}
library(psych)
describe(pokemon[,3:9])
```

### use 'data table' and 'psy::describe' for grouping describe 
```{r}
library(data.table)
as.data.table(pokemon)[,describe(Atk),by=Type.I]
```



























